Untitled

### 2023-04-13 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
edits for final sub

-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape. We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum. However, we ended up groupping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig. 1).

```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig. 1.}  Main floral morphologies considered in this study. All species were groupped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
knitr::include_graphics("../Images/flower_shapes.png")
```

>>>>

-	Flower morphology: We looked for images and illustrations of the flowers from the different species on the floras and available resources in order to categorize the flower shape. We divided the flowers in 8 main different categories: open, bowl, tube, campanulate, funnelform, papilionaceous, brush and capitulum. However, we ended up grouping all flowers on the following 6  morphological groups for analyses: tube, papilonaceous, open, capitulum, campanulate and brush (Supplementary Information Text Fig. 1).

```{r pressure, echo=FALSE, fig.cap="", out.width = '65%',fig.align='center', fig.cap="\\textbf{Supplementary Information Text Fig. 1.}  Main floral morphologies considered in this study. All species were grouped within these categories for analysis: (a) tube, (b) papilonaceous, (c) open, (d) capitulum, (e) campanulate and (f) brush."}
knitr::include_graphics("../Images/flower_shapes.png")
```
